%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV LaTeX Template for CV/Resume
%
% This template has been downloaded from:
% https://github.com/posquit0/Awesome-CV
%
% Author:
% Claud D. Park <posquit0.bj@gmail.com>
% http://www.posquit0.com
%
%
% Adapted to be an Rmarkdown template by Mitchell O'Hara-Wild
% 23 November 2018
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%
%-------------------------------------------------------------------------------
% CONFIGURATIONS
%-------------------------------------------------------------------------------
% A4 paper size by default, use 'letterpaper' for US letter
\documentclass[11pt,a4paper,]{awesome-cv}

% Configure page margins with geometry
\usepackage{geometry}
\geometry{left=1.4cm, top=.8cm, right=1.4cm, bottom=1.8cm, footskip=.5cm}


% Specify the location of the included fonts
\fontdir[fonts/]

% Color for highlights
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight

\definecolor{awesome}{HTML}{414141}

% Colors for text
% Uncomment if you would like to specify your own color
% \definecolor{darktext}{HTML}{414141}
% \definecolor{text}{HTML}{333333}
% \definecolor{graytext}{HTML}{5D5D5D}
% \definecolor{lighttext}{HTML}{999999}

% Set false if you don't want to highlight section with awesome color
\setbool{acvSectionColorHighlight}{true}

% If you would like to change the social information separator from a pipe (|) to something else
\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad}

\def\endfirstpage{\newpage}

%-------------------------------------------------------------------------------
%	PERSONAL INFORMATION
%	Comment any of the lines below if they are not required
%-------------------------------------------------------------------------------
% Available options: circle|rectangle,edge/noedge,left/right

\name{}{Cody B. Buehler}


\mobile{816-558-2679}
\email{\href{mailto:cb12991@me.com}{\nolinkurl{cb12991@me.com}}}
\homepage{codybuehler.me}
\github{cb12991}
\linkedin{codybuehler}

% \gitlab{gitlab-id}
% \stackoverflow{SO-id}{SO-name}
% \skype{skype-id}
% \reddit{reddit-id}


\usepackage{booktabs}

\providecommand{\tightlist}{%
	\setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}

%------------------------------------------------------------------------------



% Pandoc CSL macros
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{2em}
\newenvironment{CSLReferences}[3] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1 \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces\fi
  % set entry spacing
  \ifnum #2 > 0
  \setlength{\parskip}{#2\baselineskip}
  \fi
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{\honortitlestyle{#1}}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{\honordatestyle{#1}}}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}

\begin{document}

% Print the header with above personal informations
% Give optional argument to change alignment(C: center, L: left, R: right)
\makecvheader

% Print the footer with 3 arguments(<left>, <center>, <right>)
% Leave any of these blank if they are not needed
% 2019-02-14 Chris Umphlett - add flexibility to the document name in footer, rather than have it be static Curriculum Vitae
\makecvfooter
  {January 2023}
    { Cody B. Buehler~~~·~~~Resume}
  {\thepage}


%-------------------------------------------------------------------------------
%	CV/RESUME CONTENT
%	Each section is imported separately, open each file in turn to modify content
%------------------------------------------------------------------------------



\hypertarget{work-experience}{%
\section{Work Experience}\label{work-experience}}

\begin{cventries}
    \cventry{Sr. Actuarial Associate - Experience Studies and Assumption Setting, Corporate Actuarial}{Ameritas Life Insurance Corporation - Full Time}{Lincoln, Nebraska}{October 2021 – Present}{\begin{cvitems}
\item Review corporate assumptions in-depth.
\item Develop enhancements to current assumptions using machine learning or  applied statistical theory.
\item Assist interns with annual updates of corporate assumptions.
\end{cvitems}}
    \cventry{Actuarial Associate - Experience Studies and Assumption Setting, Corporate Actuarial}{}{}{September 2020 - October 2021}{\begin{cvitems}
\item Ran multi-year experience studies for life and annuity products.
\item Update corporate assumptions using current econmic and company data.
\item Propose recommendations to corporate subcommittee.
\end{cvitems}}
    \cventry{Actuarial Assistant - Valuation, Corporate Actuarial}{}{}{June 2017 – September 2020}{\begin{cvitems}
\item Assisted valuation team with annual and quarterly reporting obligations.
\item Compiled monthly in-force report to company officials and associates.
\item Responded to industry survey requests as well as internal/external audits.
\end{cvitems}}
    \cventry{Underwriting Coordinator - Business Development Underwriting}{}{}{July 2016 - June 2017}{\begin{cvitems}
\item Coordinated delivery of required documents for group dental and vision insurance requests for proposal.
\item Developed macros to help team reduce turn-around-times and a front-end GUI, back-end database for the tracking of sold cases.
\end{cvitems}}
    \cventry{Sacker/Cashier/Stocker/Grocery Clerk/Meat Cutter}{Roger’s Green Hills - Part Time Academic Year/Full Time}{St. Joseph, Missouri}{June 2007 – August 2016}{\begin{cvitems}
\item Provided excellent customer service for customers.
\item Progressed through multiple departments, each having additional responsibilities.
\item Guided new employees during the onboarding process.
\end{cvitems}}
\end{cventries}

\hypertarget{education}{%
\section{Education}\label{education}}

\begin{cventries}
    \cventry{Master of Science - Actuarial Science Major, Statistics \& Finance Minors}{University of Nebraska - Lincoln}{Lincoln, Nebraska}{August 2016 - May 2018}{}\vspace{-4.0mm}
    \cventry{Bachelor of Science - Mathematics Major}{Missouri Western State University}{St. Joseph, Missouri}{August 2011 - May 2015}{}\vspace{-4.0mm}
\end{cventries}

\hypertarget{technical-skills}{%
\section{Technical Skills}\label{technical-skills}}

\begin{cventries}
    \cventry{}{Programming Languages}{}{}{\begin{cvitems}\vspace{-4.0mm}
\item Specializing in R.
\item Proficient in Python, SQL, VBA, Markdown, and Git.
\item Experience with Java, Bash/shell scripting, M (PowerQuery), LaTeX, and HTML.
\end{cvitems}}
    \cventry{}{Package Development}{}{}{\begin{cvitems}\vspace{-4.0mm}
\item Author/maintainer of R package `expstudy` (available on CRAN).
\item Author/maintainer of R packages `cbmisc`, `wrecipe`, and other proprietary company packages.
\end{cvitems}}
    \cventry{}{Software}{}{}{\begin{cvitems}\vspace{-4.0mm}
\item Proficient in all Microsoft Office applications including PowerPivot and PowerQuery.
\item Exposed to actuarial modeling softwares MG-ALFA and Prophet as well as statistical softwares SAS and Minitab.
\end{cvitems}}
\end{cventries}

\hypertarget{volunteer-positions}{%
\section{Volunteer Positions}\label{volunteer-positions}}

\begin{cventries}
    \cventry{Builder}{Habitat for Humanity}{Lincoln, Nebraska}{January 2018}{\begin{cvitems}
\item Helped paint newly constructed residences for community members in need.
\end{cvitems}}
    \cventry{Companion}{Camp Quality}{Kansas City, Missouri}{June 2015}{\begin{cvitems}
\item Engaged children who have had or have cancer in fun activities striving to let kids with cancer be kids again.
\end{cvitems}}
\end{cventries}



\end{document}
